Notes and code examples to accompany "If the Null Fits, You Must Omit

### 2025-12-10 index.qmd
continued restructuring
ready to ship online gh-pages supplement

---
title: Notes and code examples to accompany "If the Null Fits, You Must Omit"
author: Matt Turner · [https://mat.phd](https://mat.phd)
date: today
toc: true
editor: 
  markdown: 
    wrap: 90
bibliography: "paper/this.bib"

@@

## Purpose: demonstrate gp-stats codebase

Here are some quick notes on the group polarization codebase in R supporting our article,
*If the Null Fits, You Must Omit*. The code is permanently [hosted on
GitHub](https://github.com/mt-digital/gp-statmod/tree/final-draft/GroupPolarizationStatmod).

@@

I developed two models of group polarization to serve complementary purposes.

@@

![**Mean group opinions pre- and post-discussion from Moscovici & Zavalloni
(1969).**](code_examples_images/clipboard-1443885641.png){width="575"}

>>>>

---
title: Notes and code examples to accompany "If the Null Fits, You Must Omit"
author: Matt Turner · [Email Me!](mailto:matt@mat.phd) · [https://mat.phd](https://mat.phd) 
date: today
toc: true
toc-expand: 2
editor: 
  markdown: 
    wrap: 90
bibliography: "this.bib"

@@

## Overview

Here are some quick notes on the group polarization codebase in R supporting our article,
*If the Null Fits, You Must Omit*. The code is [hosted on
GitHub](https://github.com/mt-digital/gp-statmod/tree/final-draft/GroupPolarizationStatmod).

@@

I developed two models of experimental observations in group polarization experiments
to serve complementary purposes. First is the _expectation_ model where we model the observation of the mean

@@

![**Mean group opinions pre- and post-discussion from Moscovici & Zavalloni
(1969).**](images/clipboard-1443885641.png){width="575"}
